The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-11-15 outputs/docs/events/paper.Rmd
Update paper

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how discussion in the Australian Federal Parliament changes in response to elections and changed governments. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in government are rarely associated with topic changes. The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. This has implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text-as-data, Australian political history, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

@@

We find that: firstly changes in government tend be associated with topic changes even when the party in power does not change. For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power. Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the government was returned yet there was a significant change in topics. Finally, economic events, such as financial crises, have less significant effects than other events such as terrorism.

As our dataset covers 117 years we are able to see how the effect of events changes over time. We find that the events that we are interested in are rarely significant in the first half of our dataset. With a small number of exceptions, even changes of government where the party in power also changed were not associated with overly large changes in parliamentary discussion. If governments try to more thoroughly distinguish themselves from their predecessor then longer-term policy may be more difficult to enact. Similarly, there is the danger that larger-scale signature-accomplishments of a government may be neglected by their successor for solely political reasons.

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to statistical methods, rather than requiring separate analysis. This literature sits across and draws from various historically-separate disciplines including applied statistics, economics, and political science. We contribute to this literature in terms of both data and methods. From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament on a daily basis, and we make our dataset available to other researchers via the R package \texttt{hansardr}. From a methods perspective, our analysis model has several advantages over existing methods. These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this quantitative social sciences approach to text to only increase and we expect the data and methods in our paper will be extended by other researchers in a variety of ways.

@@

We use the official PDF release and the formatting of the Hansard records changes over time. We use scripts written in R, @R2018, to convert the PDFs into daily text records. An example of the workflow and some pseudo-code are provided in Appendix \@ref(hansardworkflow). Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are corrected when they can be identified.

@@

We first use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time. We consider these topic distributions as inputs that can be analysed within another model. Thus, the second modeling step involves using a Bayesian hierarchical Dirichlet model to analyse changes in the topic distributions (obtained from the first step) in relation to events of interest.

@@

## Overview of topic modeling
Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics. This means that each day's Hansard record needs to be classified by its topics. Sometimes Hansard records includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.

@@

In order to effectively categorise topics over the whole period covering Hansard, we chose to use topic modeling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts. In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.

@@

Once government and election effects have been taken into consideration, some days stand out compared with others in their sitting period. We do not explicitly include them in the model because of over-fitting and effect-type concerns, but we are interested to see if these can be explained by events that occured on or before that sitting day. For instance, we may expect that events of a historical magnitude, such as the 9/11 attacks would be the focus of an entire day's discussion, or that the sitting day when the Apology to the Stolen Generation was delivered, or some particular legislation introduced, would be different to others in that sitting period.

@@

key_events_results %>%
  kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
  kable_styling(font_size = 10)

@@

The Second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government. The Chifley Government had governed through the end of World War II and the difficult economic times that followed. There was also a large increase in the number of seats in the House of Representatives at the 1949 election. Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics. The sixteen-year length of the Second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different. There were six elections within the Second Menzies Government. Three toward the middle of that government were associated with significant changes in the topics discussed.

@@

To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years. However the change in 1998 and 2004 is more unexpected. Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.

One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent. The results of this reduction in supervision are promising, but suggest the specifics of our process may need further refinement. For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively. It also appropriately identifies some of other key events in Australian history, such as X and Y. There are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising. When we dig into this we find that some of them, such as X and Y, are associated with significant legislation. Further work is needed to improve this approach. For instance, our approach may not be appropriately considering step-changes.

@@

The way that we identify unusual periods could also be improved. We defined sitting periods in a constant fashion across the whole dataset time frame, but how long the stretches are that parliament sits for has changed over time. In addition, more work needs to be done on how to identify outlying events. For instance, the extent to which an important event that occurs outside a sitting period can be identified has a great deal of uncertainty. And if an event happens in the middle of an sitting period, it may have a large effect on the overall mean, such that specific days are not identified as significantly outlying.

Finally, the current modelling and analysis set-up is a two-stage process: we take the output of a topic model, and use this as the input to a second model. However, this approach does not appropriately propagate uncertainty in topic distribution estimation. Future methodological work could consider how to combine these two modelling steps by extending the STM approach into a more flexible framework.

Watching our politicians at work can sometimes be a little disheartening. It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that we voted to put them there. Nonetheless, our work suggests that reasonable debate of important topics does occur in parliament. It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception. However, we do find that since the 1980s differences between government and election periods are greater than they used to be. It is, of course, reasonable that a government should act on the mandate they receive, but it takes a long time to get policy right, and we may find progress being held back if the media and political cycles become too focused on short-term events.

@@

## Example Hansard PDF to text record workflow {#hansardworkflow}
The exact scripts that we use are too long to provide here but are available on request. Instead here we provide shorterned pseudo-code that summarises the workflow to convert the PDFs to usable text datasets and may be a useful starting point for other researchers. The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018. The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014. The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.

The first step is scrape the websites for the PDFs.

```{r scrapingexample, echo=TRUE, eval = FALSE}
visit_address_and_save_PDF <-
  function(name_of_address_to_visit,
           name_of_where_to_save) {
    # Do the actual downloading of the PDF
    download.file(name_of_address_to_visit, name_of_where_to_save)
    # Helpful so that you know progress when running it on all the records
    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  
    # Space out your requests so you don't overwhelm the website
    Sys.sleep(sample(15:30, 1)) 
  }
```

The next step is remove the front matter from the PDFs.

```{r frontmatterexample, echo=TRUE, eval = FALSE}

get_text_from_PDFs <-
  function(name_of_input_PDF_file,
           name_of_output_csv_file) {
    pdf_document <- pdf_text(name_of_input_PDF_file)
    # Convert to tibble so that tidyverse can be used
    pdf_document_tibble <- tibble(text = pdf_document)
    rm(pdf_document)
    # Each row is now a page of the PDF
    # Adding a column of the row numbers allows you to keep track of the page numbers
    pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble)
    # Separate each line (of each page) into own row
    pdf_document_tibble <-
      separate_rows(pdf_document_tibble, text, sep = "\\n")
    # Identify page headers and footers and remove them
    pdf_document_tibble <- pdf_document_tibble %>%
      group_by(pageNumbers) %>%
      mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page
      mutate(lastLine = n()) %>% # This tells you the number of the last line in each page
      ungroup()
    ## Identify front matter and remove it
    pdf_document_tibble <- pdf_document_tibble %>%
      mutate(
        firstSpeakerRow = str_detect(text, "SPEAKER")
      )
    pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA
    # Get the row and corresponding page and then filter to only pages from that page
    row_of_first_SPEAKER <-
      pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first()
    first_page_of_interest_SPEAKER <-
      pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer()
    filter_from_here <-
      case_when(
        !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER
      )
    pdf_document_tibble <- pdf_document_tibble %>%
      filter(pageNumbers >= filter_from_here) %>%
      select(-firstSpeakerRow)
    # Save file
    write_csv(pdf_document_tibble, name_of_output_csv_file)
    # Helpful to know where you're up to
    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
  }

Then the rows need to be combined:
```{r combinerows, echo=TRUE, eval = FALSE}
split_columns <-
  function(name_of_input_csv_file,
           name_of_output_csv_file) {
    # Read in the csv, based on the filename list
    csv_with_rows_to_combine <-
      read_csv(name_of_input_csv_file,
               trim_ws = FALSE,
               col_types = cols())
    # Remove any extra whitespace i.e. two or more spaces and spaces at either end. 
    # Yes, I know that I turned this off in the read_csv, but it's better to be 
    #explicit because the whitespace is useful sometimes.
    csv_with_rows_to_combine$text <-
      str_squish(csv_with_rows_to_combine$text)
    # Put everything onto one line, which allows us to rejoin words that have been 
    #split across two lines e.g. Mon- ica
    csv_with_rows_to_combine <- csv_with_rows_to_combine %>%
      mutate(text = str_replace_all(text, "-$", "MONICA"))
    full_days_hansard <- csv_with_rows_to_combine %>%
      select(-pageNumbers) %>%
      summarise(text = paste(text, collapse = " ")) %>%
      mutate(text = str_replace_all(text, "MONICA ", "")) %>%
      mutate(text = str_replace_all(text, "[:space:]-(?=[:alpha:])", " - "))
    rm(csv_with_rows_to_combine)
    write_csv(full_days_hansard, name_of_output_csv_file)
    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
  }
```

Finally, we can fix the spelling:
```{r fixspelling, echo=TRUE, eval = FALSE}
fix_spelling <-
  function(name_of_input_csv_file,
           name_of_output_csv_file) {
    csv_to_clean <-
      read_csv(name_of_input_csv_file,
               trim_ws = FALSE,
               col_types = cols())
    #Fix the spelling
    csv_to_clean$text <-
      stri_replace_all_regex(
        csv_to_clean$text,
        "\\b" %s+% fix_wrong_spellings$original %s+% "\\b",
        fix_wrong_spellings$corrected,
        vectorize_all = FALSE
      )
    # Save file
    write_csv(csv_to_clean, name_of_output_csv_file)
    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
  }
```

@@

## Stopwords over time {#stopwordsgraph}
Insert the graph of stop words over time.

@@

The choice of the number of topics to use in a topic model has a substantial affect on the results of the model. For instance, in our topic model, choosing a smaller number of topics, such as 10 or 20 results in a model that is not all that useful because the topics are so broad.

There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice, especially at a more fine level such as choosing betweeen 60 and 65 topics. We found it useful to try a few quite different measures before settling on 80 topics. This provided a balance between being granular enough to be informative--anything less than 40 topics tended to be too broad-- yet still being tractable for our analysis model in a reasonable amount of time. In addition to looking at the topics and how they changed over time, diagnostic measures that we considered include the held-out likelihood, the lower bound, residuals, exclusivity. and semantic coherence (Figures \@ref(fig:topicsdiagnostics)).[^Silgefootnote]

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how discussion in the Australian Federal Parliament changes in response to elections and changed governments. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in government are rarely associated with topic changes. The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. This has implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text-as-data, Australian political history, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

key_events_results_cols <-
  read_csv(here::here("outputs/results-analysis_model/results-outliers_in_columns.csv"), col_types = cols())

names(key_events_results_cols) <- c("Dates", "", "", "", "", "", "", "")

@@

We find that: firstly, changes in government tend be associated with topic changes even when the party in power does not change. For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power. Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the government was returned yet there was a significant change in topics. Finally, economic events, such as financial crises, have less significant effects than other events such as terrorism.

As our dataset covers 117 years we are able to see how the effect of events changes over time. We find that the events that we are interested in are rarely significant in the first half of our dataset. With a small number of exceptions, even changes of government where the party in power also changed were not associated with overly large changes in parliamentary discussion. If governments try to more thoroughly distinguish themselves from their predecessor, then longer-term policy may be more difficult to enact. Similarly, there is the danger that larger-scale signature-accomplishments of a government may be neglected by their successor for solely political reasons.

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to statistical methods, rather than requiring separate analysis. This literature sits across and draws from various historically-separate disciplines including applied statistics, economics, and political science. We contribute to this literature in terms of both data and methods. From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament on a daily basis, and we make our dataset available to other researchers via the R package \texttt{hansardr}. From a methods perspective, our analysis model has several advantages over existing methods. These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in a quantitative approach to text to only increase and the data and methods in our paper will be extended in a variety of ways.

@@

We use the official PDF release and the formatting of the Hansard records changes over time. We use scripts written in R, @R2018, to convert the PDFs into daily text records. An example of the workflow and some example scripts are provided in Appendix \@ref(hansardworkflow). Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are corrected when they can be identified.

@@

We first use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time. We consider these topic distributions as inputs that can be analysed within another model. Thus, the second modelling step involves using a Bayesian hierarchical Dirichlet model to analyse changes in the topic distributions (obtained from the first step) in relation to events of interest.

@@

## Overview of topic modelling
Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics. This means that each day's Hansard record needs to be classified by its topics. Sometimes Hansard records includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.

@@

In order to effectively categorise topics over the whole period covering Hansard, we chose to use topic modelling , a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts. In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.

@@

Once government and election effects have been taken into consideration, some days stand out compared with others in their sitting period. We do not explicitly include them in the model because of over-fitting and effect-type concerns, but we are interested to see if these can be explained by events that occurred on or before that sitting day. For instance, we may expect that events of a historical magnitude, such as the 9/11 attacks would be the focus of an entire day's discussion, or that the sitting day when the Apology to the Stolen Generation was delivered, or some particular legislation introduced, would be different to others in that sitting period.

@@

key_events_results_cols %>%
  kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
  kable_styling(font_size = 10)

@@

The Second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government. The Chifley Government had governed through the end of World War II and the difficult economic times that followed. There was also a large increase in the number of seats in the House of Representatives at the 1949 election. Many new politicians entered parliament, and this changed representation may also have been partly to do with the changed distribution of discussion topics. The sixteen-year length of the Second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different. There were six elections within the Second Menzies Government. Three toward the middle of that government were associated with significant changes in the topics discussed.

@@

To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years. However, the change in 1998 and 2004 is more unexpected. Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.

One advantage of our analysis model compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent. The results of this reduction in supervision are promising, but suggest the specifics of our process may need further refinement. For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively. But there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising. When we dig into this we find that some of them, such as 4 February 2009, are associated with significant legislation. However the over-weighting of dates in the first half of our sample in Table \@ref(tab:keyeventsresultstable) highlights further work is needed to improve this approach. For instance, our approach may not be appropriately considering step-changes or it may be that our identification of sitting periods is not appropriate for the entire period.

@@

The way that we identify unusual periods could also be improved. We defined sitting periods in a constant fashion across the whole dataset time frame, but how long the stretches are that parliament sits for has changed over time. In addition, more work needs to be done on how to identify outlying events. For instance, the extent to which an important event that occurs outside a sitting period can be identified has a great deal of uncertainty. And if an event happens in the middle of a sitting period, it may have a large effect on the overall mean, such that specific days are not identified as significantly outlying.

Finally, the current modelling and analysis set-up is a two-stage process: we take the output of a topic model, and use this as the input to a second model. However, this approach does not appropriately propagate the uncertainty of the topic distribution estimation stage. Future methodological work could consider how to combine these two modelling steps, for instance by extending the STM approach into a more flexible framework.

Watching our politicians at work can sometimes be a little disheartening. It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that we voted to put them there. Nonetheless, our work suggests that important topics are discussed in parliament. It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception. However, we do find that since the 1980s differences between government and election periods seem to be more pronounced than they used to be. It is, of course, reasonable that a government should act on the mandate they receive, but it takes a long time to get policy right, and we may find progress being held back if the media and political cycles become too focused on short-term events.

@@

## Example Hansard PDF to text record workflow {#hansardworkflow}
The exact scripts that we use are too long to provide here but are available on request. Instead here we provide example scripts that summarises the workflow to convert the PDFs to usable text datasets and may be a useful starting point for other researchers. The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018. The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014. The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.

**[Insert the example scripts.]**

<!-- The first step is to scrape the websites for the PDFs. -->

<!-- ```{r scrapingexample, echo=TRUE, eval = FALSE} -->
<!-- visit_address_and_save_PDF <- -->
<!--   function(name_of_address_to_visit, -->
<!--            name_of_where_to_save) { -->
<!--     # Do the actual downloading of the PDF -->
<!--     download.file(name_of_address_to_visit, name_of_where_to_save) -->
<!--     # Helpful so that you know progress when running it on all the records -->
<!--     print(paste("Done with", name_of_where_to_save, "at", Sys.time()))   -->
<!--     # Space out your requests so you don't overwhelm the website -->
<!--     Sys.sleep(sample(15:30, 1))  -->
<!--   } -->
<!-- ``` -->

<!-- The next step is to remove the front matter from the PDFs.  -->

<!-- ```{r frontmatterexample, echo=TRUE, eval = FALSE} -->

<!-- get_text_from_PDFs <- -->
<!--   function(name_of_input_PDF_file, -->
<!--            name_of_output_csv_file) { -->
<!--     pdf_document <- pdf_text(name_of_input_PDF_file) -->
<!--     # Convert to tibble so that tidyverse can be used -->
<!--     pdf_document_tibble <- tibble(text = pdf_document) -->
<!--     rm(pdf_document) -->
<!--     # Each row is now a page of the PDF -->
<!--     # Adding a column of the row numbers allows you to keep track of the page numbers -->
<!--     pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble) -->
<!--     # Separate each line (of each page) into own row -->
<!--     pdf_document_tibble <- -->
<!--       separate_rows(pdf_document_tibble, text, sep = "\\n") -->
<!--     # Identify page headers and footers and remove them -->
<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
<!--       group_by(pageNumbers) %>% -->
<!--       mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page -->
<!--       mutate(lastLine = n()) %>% # This tells you the number of the last line in each page -->
<!--       ungroup() -->
<!--     ## Identify front matter and remove it -->
<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
<!--       mutate( -->
<!--         firstSpeakerRow = str_detect(text, "SPEAKER") -->
<!--       ) -->
<!--     pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA -->
<!--     # Get the row and corresponding page and then filter to only pages from that page -->
<!--     row_of_first_SPEAKER <- -->
<!--       pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first() -->
<!--     first_page_of_interest_SPEAKER <- -->
<!--       pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer() -->
<!--     filter_from_here <- -->
<!--       case_when( -->
<!--         !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER -->
<!--       ) -->
<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
<!--       filter(pageNumbers >= filter_from_here) %>% -->
<!--       select(-firstSpeakerRow) -->
<!--     # Save file -->
<!--     write_csv(pdf_document_tibble, name_of_output_csv_file) -->
<!--     # Helpful to know where you're up to -->
<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
<!--   } -->

<!-- Then the rows need to be combined: -->
<!-- ```{r combinerows, echo=TRUE, eval = FALSE} -->
<!-- split_columns <- -->
<!--   function(name_of_input_csv_file, -->
<!--            name_of_output_csv_file) { -->
<!--     # Read in the csv, based on the filename list -->
<!--     csv_with_rows_to_combine <- -->
<!--       read_csv(name_of_input_csv_file, -->
<!--                trim_ws = FALSE, -->
<!--                col_types = cols()) -->
<!--     # Remove any extra whitespace i.e. two or more spaces and spaces at either end.  -->
<!--     # Yes, I know that I turned this off in the read_csv, but it's better to be  -->
<!--     #explicit because the whitespace is useful sometimes. -->
<!--     csv_with_rows_to_combine$text <- -->
<!--       str_squish(csv_with_rows_to_combine$text) -->
<!--     # Put everything onto one line, which allows us to rejoin words that have been  -->
<!--     #split across two lines e.g. Mon- ica -->
<!--     csv_with_rows_to_combine <- csv_with_rows_to_combine %>% -->
<!--       mutate(text = str_replace_all(text, "-$", "MONICA")) -->
<!--     full_days_hansard <- csv_with_rows_to_combine %>% -->
<!--       select(-pageNumbers) %>% -->
<!--       summarise(text = paste(text, collapse = " ")) %>% -->
<!--       mutate(text = str_replace_all(text, "MONICA ", "")) %>% -->
<!--       mutate(text = str_replace_all(text, "[:space:]-(?=[:alpha:])", " - ")) -->
<!--     rm(csv_with_rows_to_combine) -->
<!--     write_csv(full_days_hansard, name_of_output_csv_file) -->
<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
<!--   } -->
<!-- ``` -->

<!-- Finally, we can fix the spelling: -->
<!-- ```{r fixspelling, echo=TRUE, eval = FALSE} -->
<!-- fix_spelling <- -->
<!--   function(name_of_input_csv_file, -->
<!--            name_of_output_csv_file) { -->
<!--     csv_to_clean <- -->
<!--       read_csv(name_of_input_csv_file, -->
<!--                trim_ws = FALSE, -->
<!--                col_types = cols()) -->
<!--     #Fix the spelling -->
<!--     csv_to_clean$text <- -->
<!--       stri_replace_all_regex( -->
<!--         csv_to_clean$text, -->
<!--         "\\b" %s+% fix_wrong_spellings$original %s+% "\\b", -->
<!--         fix_wrong_spellings$corrected, -->
<!--         vectorize_all = FALSE -->
<!--       ) -->
<!--     # Save file -->
<!--     write_csv(csv_to_clean, name_of_output_csv_file) -->
<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
<!--   } -->
<!-- ``` -->

@@

## Stopwords over time {#stopwordsgraph}
**[Insert the graph of stop words over time.]**

@@

The choice of the number of topics to use in a topic model has a substantial effect on the results of the model. For instance, in our topic model, choosing a smaller number of topics, such as 10 or 20 results in a model that is not all that useful because the topics are so broad.

There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice, especially at a finer level such as choosing between 60 and 65 topics. We found it useful to try a few quite different measures before settling on 80 topics. This provided a balance between being granular enough to be informative--anything less than 40 topics tended to be too broad-- yet still being tractable for our analysis model in a reasonable amount of time. In addition to looking at the topics and how they changed over time, diagnostic measures that we considered include the held-out likelihood, the lower bound, residuals, exclusivity. and semantic coherence (Figures \@ref(fig:topicsdiagnostics)).[^Silgefootnote]
